---
title: 'Psych 251 PS4: Simulation'
author: "Ellen Reinhart"
date: "2018"
output: 
  html_document:
    toc: true
---

>Ellen's note re: collaboration: I worked on this problem set with Andrew, Luiza, Marianna, Lauren, and Julie. The work is my own, but we brainstormed, did troubleshooting, and tested different strategies together. 

This is problem set #3, in which we want you to integrate your knowledge of data wrangling with some basic simulation skills and some linear modeling.

For ease of reading, please separate your answers from our text by marking our text with the `>` character (indicating quotes). 

```{r}
library(tidyverse)
```

Let's start by convincing ourselves that t-tests have the appropriate false positive rate. Run 10,000 t-tests with standard, normally-distributed data from a made up 30-person, single-measurement experiment (the command for sampling from a normal distribution is `rnorm`). What's the mean number of "significant" results?

First do this using a `for` loop.

```{r}
sig_results <- 0

for(i in 1:10000) {
  p_val <- t.test(rnorm(30))$p.value
  sig <- p_val < .05
  if(p_val < .05) sig_results = sig_results + 1
}

print(sig_results)
```

> Roughly 500 out of the 10,000 trials (5%) are significant. 

Next, do this using the `replicate` function:

```{r}

sig_num <- replicate(10000, t.test(rnorm(30))$p.value < .05)
sum(sig_num)

```

Ok, that was a bit boring. Let's try something more interesting - let's implement a p-value sniffing simulation, in the style of Simons, Nelson, & Simonsohn (2011).

Consider this scenario: you have done an experiment, again with 30 participants (one observation each, just for simplicity). The question is whether their performance is above chance. You aren't going to check the p-value every trial, but let's say you run 30 - then if the p-value is within the range p < .25 and p > .05, you optionally run 30 more and add those data, then test again. But if the original p value is < .05, you call it a day, and if the original is > .25, you also stop.  

First, write a function that implements this sampling regime.

```{r}
double.sample <- function (){
  x = rnorm(30)
  p_val <- t.test(x)$p.value
  if(p_val < .25 & p_val > .05){
    x = c(x,rnorm(30))
  p_val <- t.test(x)$p.value  
  }
  return(p_val)
}
```

Now call this function 10k times and find out what happens. 

```{r}

results <- replicate(10000, double.sample() < 0.05)
sum(results)

```

Is there an inflation of false positives? How bad is it?

> Yes. The rate of false positives increases from ~500 to ~700, which is about a 40% increase in false positives. 

Now modify this code so that you can investigate this "double the sample" rule in a bit more depth. Let's see what happens when you double the sample ANY time p > .05 (not just when p < .25), or when you do it only if p < .5 or < .75. How do these choices affect the false positive rate?

HINT: Try to do this by making the function `double.sample` take the upper p value as an argument, so that you can pass this through dplyr.

HINT 2: You may need more samples. Find out by looking at how the results change from run to run.

```{r}
#learning to feed in different high p values 
double.sample <- function (upper){
  x = rnorm(30)
  p_val <- t.test(x)$p.value
  if(p_val < upper & p_val > .05){
    x = c(x,rnorm(30))
  p_val <- t.test(x)$p.value  
  }
  return(p_val)
}

results <- replicate(10000, double.sample(.1) < 0.05)
sum(results)
```

What do you conclude on the basis of this simulation? How bad is this kind of data-dependent policy?

> When the condition is only p > .05, the sum increases to ~800, which is a 60% increase in false positive rates.When p > .5, the sum is ~820, and when p > .75 the sum is ~830. As the p-value threshold for increasing the sample increases, so does the false positive rate. It appears to be asymptotic, so that as the p-value threshold gets higher, the effect on the false positive rate levels off. Given that NHST operates on the condition that the false positive rate is 5%, it's clear that a data-dependent sampling policy negates that assumption and biases data. I'm interested in hearing the teaching team's thoughts on p < .1 as marginally significant. I've run the simulation with the upper limit p value as .1, and the number of false positives increases to ~580, which is a 16% increase in false positives (but it's also increasing from 5% to 5.8% chance of false positives). Data-dependent policies clearly bias data, but this also makes me think about what to make of findings that are marginal, given that there's a higher chance that there's a 5.8% probability of a false positive compared to less than 5% probability with the traditional p < .05 cutoff. 



















